---
title: "Week6_homework"
author: "Heather"
date: "3/3/2022"
output:
  prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "../Outputs/", echo = TRUE, warning = FALSE, message = FALSE)
```

## Introduction

Today we are going to practice **RMarkdown** using the *Palmer Penguins* data.

## Loading libraries
```{r}
library(tidyverse)
library(here)
library(palmerpenguins)
library(kableExtra)
library(palettetown)
```

## Inspecting the data

Let's take a quick look at the Palmer Penguins data frame.

```{r}
glimpse(penguins)
```

## Making a table

This data set includes three species of penguins:

* Adelie
* Gentoo
* Chinstrap

Penguins were examined on three islands:

* Dream
* Torgersen
* Biscoe

Let's look at the mean and variance of *flipper length* for each penguin species living on each island. **Gentoo** penguins on **Biscoe** have the largest mean flipper length. 

```{r, echo=FALSE}
penguins %>%  #Using penguins data frame
  group_by(species, island) %>%  #Grouping by species and island
  summarise(mean = mean(flipper_length_mm, #Using summary to calculate mean flipper length
                        na.rm = TRUE), #Removing NAs
            variance = var(flipper_length_mm, #Calculating variance in flipper length
                           na.rm = TRUE)) %>% #Removing NAs
  kbl() %>%  #Make it a kable table
  kable_classic()%>%  #Using the kable classic theme
  row_spec(5, bold = T, background = "palegreen") %>% #Changing row 5 to have bold text and green background
  kable_styling(bootstrap_options = "striped", #Making alternate rows gray
                full_width = FALSE) #Making the width smaller than the entire page
```

## Making a plot

Let's make a plot to examine **flipper length (mm)** for each species living on each island for each sex.

```{r Week6_homework_plot, out.width="70%", fig.asp=0.8, fig.align='center', echo=FALSE}
penguins %>%  #Using penguins data frame
  drop_na(sex, flipper_length_mm) %>% #dropping NA values from sex and flipper length
  ggplot(mapping = aes(x = sex, #Mapping sex to x axis
                       y = flipper_length_mm, #Mapping flipper length to y axis
                       fill = species)) + #Mapping fill color to species
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) + #Violin geometry with quantiles
  facet_wrap(~island) + #Facet wrapping for island
  theme_gray() + #Changing theme
  scale_fill_manual(values = pokepal(134)) +  #Changing fill color palette
  labs(title = "Flipper Length (mm) vs. Sex", #Adding title to plot
       subtitle = "Flipper length by sex for penguins living on Biscoe, Dream, and Torgersen Islands", #Adding subtitle
       y = "Flipper Length (mm)", #Changing y axis title
       x = "Sex", #Changing x axis title
       caption = "Source: Palmer Station LTER / palmerpengins package") #Adding a caption with data source
```

