---
title: "Week7_homework"
author: "Heather"
date: "3/8/2022"
output: 
  html_document:
    theme: cerulean
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "../Outputs/", echo = TRUE, warning = FALSE, message = FALSE)
```

Today we are going to practice making a map.  
Created by: Heather Carstensen  
Updated on: 2022-03-08  

## Load Libraries  

```{r}
library(tidyverse)
library(here)
library(maps)
library(mapdata)
library(mapproj)
```

## Load Data - Meteorite Impacts  
Read in the meteorite impact data from the Tidy Tuesday repository. This data frame was used for TidyTuesday 2019-06-11.

```{r}
meteorites <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-11/meteorites.csv")
```

## Setting Up Data Frames  
Filtering the world map data to just include Australia and New Zealand. 

```{r}
world<-map_data("world")  #Bringing in world map data

Aust_NZ <- world %>% 
  filter(region == c("Australia", "New Zealand")) #Filtering to Australia and New Zealand
```


## Making a map  
Using ggplot geoms polygon and point to make a map of Australia and New Zealand showing meteorite impacts, with color representing mass of the meteorite. 

```{r, Week7_homework_map}
ggplot()+  #Starting plot
  geom_polygon(data = Aust_NZ, #Using the Australia/New Zealand data for polygon geometry to make a map
               aes(x = long, #Mapping longitude to x-axis
                   y = lat, #Mapping latitude to y-axis
                   group = group),  #Mapping group = group
               color = "black",  #Making region outlines black
               fill = "lightgray")+  #Changing polygon fill color
  geom_point(data = meteorites, #Layering on point geometry using meteorite impact data
             aes(x = long, #Mapping longitude to x-axis
                 y = lat,  #Mapping latitude to y-axis
                 color = mass)) +  #Mapping color to mass of meteorite
  scale_color_viridis_c(trans = "log10") +  #Changing color for meteorite mass to use viridis
  theme(panel.background = element_rect(fill = "lightskyblue1"),  #Changing the background color to blue
        panel.grid.major = element_line(size = 0.2)) +  #Reducing size of the grid lines
  scale_x_continuous(breaks = scales::breaks_width(10)) +  #Making the grid line breaks every 10 degrees
  scale_y_continuous(breaks = scales::breaks_width(10)) +  #Making the grid line breaks every 10 degrees
  coord_map(projection = "mercator", #Changing projection to mercator
            xlim = c(100,180),  #Zooming in to this range for longitude
            ylim = c(-50,0)) +  #Zooming in to this range for latitude
  labs(x = "Longitude",  #Changing x-axis lable
       y = "Latitude", #Changing y-axis lable
       title = "Meteorite Impacts by Mass in Australia and New Zealand",  #Adding a title
       caption = "Data from the Meteoritical Society by way of NASA",  #Adding a caption with data source
       color = "Mass (g)")  #Changing legend title
```



