---
title: "Week 7 Homework B"
author: "Heather"
date: "3/11/2022"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Good plot/Bad plot assignment using Bob Ross TidyTuesday data set from week of 2019-08-06. 

First, load the necessary libraries. 

```{r}
### Load Libraries ###

library(tidyverse)
library(here)
library(ggpubr)
library(jpeg)
```

## Loading and Viewing Data

First I will read in the data and make alterations to the data frame that were
suggested in the TidyTuesday repository. Then I will look at how many times
each painting element was included in Bob Ross's paintings in the first 10 seasons
of The Joy of Painting. This will allow me to find the top 10 elements he used
in his paintings during those seasons. 

```{r}
### Read in Data from TidyTuesday###

bob_ross <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-08-06/bob-ross.csv")

### Run the suggested code to clean up the episode information ###

bob_ross <- bob_ross %>%  #Overwriting object bob_ross
  separate(col = EPISODE,  #Separating the column EPISODE into two columns
           into = c("season", "episode"),  #Naming the two new columns
           sep = "E",  #Telling R where to separate the values
           remove = FALSE) %>%  #Don't remove the original column
  mutate(season = str_extract(season, "[:digit:]+")) %>%  #Removing the "S" from the season values so that only the number corresponding to season remains
  mutate_at(vars(season, episode), as.integer)  #Making the season and episode columns into integer columns rather than character

### Look at sum of all columns in the first 10 seasons of The Joy of Painting

bob_ross_sum <- bob_ross %>%  #New data frame 
  filter(season %in% c("1", "2", "3", "4", "5", 
                       "6", "7", "8", "9", "10")) %>% #Filtering for the first 10 seasons of the show
  summarise(across(c(5:52), sum))  #Using summarise to generate sums of column values

glimpse(bob_ross_sum)


```


## Data Wrangling

Next, I will make two data frames to use for plotting - bob_ross_messy for the "Bad Plot"
and bob_ross_clean for the "Good Plot."  
bob_ross_clean will include the total number of times the top 10 painting elements were 
included in his paintings during the first 10 seasons of The Joy of Painting, arranged 
by value
bob_ross_messy will include similar data, but not filtered to the top 10 elements, so there will be many more data points. 

```{r}
### Make a new data frame with the sum of the top 10 elements
### included in Bob Ross's paintings from the first 10 seasons of The Joy of Painting

bob_ross_clean <- bob_ross %>%  #New data frame
  filter(season %in% c("1", "2", "3", "4", "5", 
                       "6", "7", "8", "9", "10")) %>%  #Filtering for the first 10 seasons
  summarise(across(c(BUSHES, CABIN, CLOUDS, CONIFER, CUMULUS, 
                     DECIDUOUS, GRASS, LAKE, MOUNTAIN, OCEAN), sum)) %>% #Want sum of these top ten elements featured in Bob Ross's paintings
  pivot_longer(cols = BUSHES:OCEAN,  #Pivoting the data frame longer
               names_to = "Elements",  #Creating Elements column for painting elements
               values_to = "Values")   #Creating Values column for frequency of those painting elements

glimpse(bob_ross_clean)

### Make a new data frame with the sum of elements
### included in paintings from the first 10 seasons

bob_ross_messy <- bob_ross %>%  #New data frame
  filter(season %in% c("1", "2", "3", "4", "5", 
                       "6", "7", "8", "9", "10")) %>%  #Filtering to the first 10 seasons
  summarise(across(c(5:52), sum)) %>%  #Generating sum of these columns
  pivot_longer(cols = APPLE_FRAME:RECTANGULAR_FRAME,  #Pivoting the data frame longer
               names_to = "Elements",  #Creating Elements column for painting elements
               values_to = "Values")   #Creating Values column for frequency of those painting elements

glimpse(bob_ross_messy)
```

## Bad Plot

Now I will make a Bad Plot using the bob_ross_messy data frame. 

```{r}
Bob <- here("Week_7", "Data", "Bob-Ross.jpg")  #Importing an image of Bob Ross
Bob <- jpeg::readJPEG(Bob)  #Reading the image as jpeg
colors_bad <- c("chartreuse", "#FC7A57", "#C4E7D4", "khaki1", "mediumspringgreen", "mistyrose",
                "chartreuse", "#FC7A57", "#C4E7D4", "khaki1", "mediumspringgreen", "mistyrose",
                "chartreuse", "#FC7A57", "#C4E7D4", "khaki1", "mediumspringgreen", "mistyrose",
                "chartreuse", "#FC7A57", "#C4E7D4", "khaki1", "mediumspringgreen", "mistyrose",
                "chartreuse", "#FC7A57", "#C4E7D4", "khaki1", "mediumspringgreen", "mistyrose",
                "chartreuse", "#FC7A57", "#C4E7D4", "khaki1", "mediumspringgreen", "mistyrose",
                "chartreuse", "#FC7A57", "#C4E7D4", "khaki1", "mediumspringgreen", "mistyrose",
                "chartreuse", "#FC7A57", "#C4E7D4", "khaki1", "mediumspringgreen", "mistyrose") #Making a custom color palette designed for 48 bars by repeating 6 colors 8 times

bob_ross_messy %>% #Use bob_ross_messy data frame
  ggplot() +  #Start a ggplot
  background_image(Bob) +  #Include background image of Bob Ross
  geom_col(aes(x = Elements,  #Choose column geometry, and map Elements to x-axis
               y = Values),  #Map Values to y-axis
           fill = colors_bad,  #Set bar fill colors to custom palette
           color = "orange") +  #Set bar outline color
  labs(title = "Happy Little Accidents",  #Add a title
       subtitle = "The early seasons",  #Add subtitle
       x = " ",  #Remove x-axis label
       y = " ") +  #Remove y-axis label
  theme(plot.background = element_rect(fill = "darkgoldenrod4"),  #Set the plot background color
        axis.text.x = element_text(hjust = 1)) +  #Drop the x-axis labels to below the plot border
  ylim(-10, 200) #Increase the limits of the y-axis

### Save the output ###

ggsave(here("Week_7", "Outputs", "Bad_Plot.png"),
       width = 6, height = 4)

```

Why this is a Bad Plot:  

* Neither the title nor the subtitle describe the data or conclusions. 
* There is no description of where the data came from. 
* There are so many labels on the x-axis and the font is so big that the text overlaps completely. 
* There are no titles/labels for the x and y-axes.
* The panel background color make it difficult to read the axis grid labels. 
* The y-axis is too tall for the data - it should not extend that much higher than the tallest bar.
* The colors are randomly chosen and are not mapped to data. They don't match the aesthetics of the plot. They're all around the same brightness/value, making them difficult to distinguish. 
* The border color around each bar is similarly bright, and so does not help distinguish between the bars. 
* There are so many bars that the data are difficult to interpret (or would be if the x-axis could be read) - too much data has been plotted.
* The background image of Bob Ross is distracting, unnecessary, and obscures the bars and grid lines. The picture is also blurry. 
* The major y-axis marks are spaced every 50 items, but there should be more grid lines to help the reader interpret the data, such as every 10 items. 

## Good Plot

Now I will make a better plot using the bob_ross_clean data frame. I will also make a custom color palette based on the paint colors he uses in the show, but with alterations to make them brighter and easier to distinguish. 

```{r}
colors_good <- c("#598FB1", "#CA382B", "#0F1108", "#755A43", "#1D3524", 
            "#2C4FA0", "#EDAE49", "#6F1A07", "#A0AA9D", "#256D1B")  #Choose a custom color palette

bob_ross_clean %>%  #Start with bob_ross_clean data frame
  ggplot() +  #Start a ggplot
  geom_col(aes(x = Elements,  #Choose column geometry, and map Elements to x-axis
               y = Values),  #Map Values to y-axis
           fill = colors_good,  #Set the bar fill colors to the custom palette
           color = "black") +  #Set the bar outlines to black 
  theme(panel.background = element_rect(fill = "white",  #Set the plot panel background to white
                                        color = "black"),  #Set the plot panel border to black
        plot.background = element_rect(fill = "floralwhite"),  #Set the plot background to floral white
        panel.grid.major = element_line(size = 0.1, #Set the size of the major grid lines
                                        color = "black"),  #Set the color of the major grid lines to black
        axis.text.x = element_text(angle = 60, #Set the angle of the x-axis labels to 60 degrees
                                   hjust = 1)) +  #Drop the x-axis labels to below the plot border
  scale_y_continuous(breaks = scales::breaks_width(10)) +  #Make y-axis major grid lines every 10 items
  labs(title = "Frequency of top ten painting elements included in \nthe first ten seasons of Bob Ross's show, The Joy of Painting", #Add title
       x = " ", #Remove x-axis label
       y = "Count", #Change y-axis label
       caption = "Data from FiveThirtyEight via TidyTuesday week of 2019-08-06")  #Add a caption with the data source

### Save the Output ###

ggsave(here("Week_7", "Outputs", "Good_Plot.png"),
       width = 6, height = 4)
```

Why this is a Good Plot:

* The title clearly describes the data. 
* The subtitle describes where the data are from. 
* A bar chart is a reasonable choice to show this type of data. 
* The axis titles and grid labels are easy to read. 
* The scale of the axis fits the data values well - the y-axis is not too high or low. 
* The y-axis grid helps the reader see the value each bar corresponds to. 
* The bar colors vary in value, so that adjacent bars are easy to distinguish. 
* The bars are outlined in black, making their edges easy to see. 
* The background behind the bar plot is white, making the bars easily visible. 
* There are not any distracting or unnecessary graphics or plot elements. 
* The size and placement of the plot within the space makes sense - the plot is not too small and there is not too much empty space. 

